My title

### 2023-03-16 outputs/paper/Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors.qmd
data cleaning and graph

# loading in relevant libraries
library(RColorBrewer)
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)

@@

ggplot(happiness_data, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Changes in happiness levels from 1972 to 2021",
       color = "Happy level")

@@

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-2VeryHappyGender
#| fig-cap: "Trends in happiness level (very happy) by gender from 1972 to 2021"

# calculate the count of individuals for very happy level
sex_data_happy1 <- sex_data %>% 
  filter(Happy == "Very happy") %>% 
  group_by(Sex, Year, Happy) %>% 
  summarize(People = n())

# generate graph
sex_colors <- c("#E74C3C", "#2C3E50")

ggplot(sex_data_happy1, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Trends in happiness level (very happy) by gender from 1972 to 2021")

```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-3PrettyHappyGender
#| fig-cap: "Trends in happiness level (pretty happy) by gender from 1972 to 2021"

# calculate the count of individuals for pretty happy level
sex_data_happy2 <- sex_data %>% 
  filter(Happy == "Pretty happy") %>% 
  group_by(Sex, Year, Happy) %>% 
  summarize(People = n())

# generate graph
sex_colors <- c("#E74C3C", "#2C3E50")

ggplot(sex_data_happy2, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Trends in happiness level (pretty happy) by gender from 1972 to 2021")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-4NotTooHappyGender
#| fig-cap: "Trends in happiness level (not too happy) by gender from 1972 to 2021"

# calculate the count of individuals for not too happy level
sex_data_happy3 <- sex_data %>% 
  filter(Happy == "Not too happy") %>% 
  group_by(Sex, Year, Happy) %>% 
  summarize(People = n())

# generate graph
sex_colors <- c("#E74C3C", "#2C3E50")

ggplot(sex_data_happy3, aes(x = Year, y = People, fill = Sex)) +
  geom_line(aes(group = Sex, color = Sex), size = 1.2) +
  scale_fill_manual(values = sex_colors) +
  scale_color_manual(values = sex_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Sex", title = "Trends in happiness level (not too happy) by gender from 1972 to 2021")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-5VeryHappyRace
#| fig-cap: "Trends in happiness level (very happy) by race from 1972 to 2021"

# calculate the count of individuals for very happy level
race_data_happy1 <- race_data %>% 
  filter(Happy == "Very happy") %>% 
  group_by(Race, Year, Happy) %>% 
  summarize(People = n())

# generate graph
race_colors <- c("#3498DB", "#27AE60", "#F39C12")

ggplot(race_data_happy1, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Trends in happiness level (very happy) by race from 1972 to 2021")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-6PrettyHappyRace
#| fig-cap: "Trends in happiness level (pretty happy) by race from 1972 to 2021"

# calculate the count of individuals for pretty happy level
race_data_happy2 <- race_data %>% 
  filter(Happy == "Pretty happy") %>% 
  group_by(Race, Year, Happy) %>% 
  summarize(People = n())

# generate graph
race_colors <- c("#3498DB", "#27AE60", "#F39C12")

ggplot(race_data_happy2, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Trends in happiness level (pretty happy) by race from 1972 to 2021")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-7NotTooHappyRace
#| fig-cap: "Trends in happiness level (not too happy) by race from 1972 to 2021"

# calculate the count of individuals for not too happy level
race_data_happy3 <- race_data %>% 
  filter(Happy == "Not too happy") %>% 
  group_by(Race, Year, Happy) %>% 
  summarize(People = n())

# generate graph
race_colors <- c("#3498DB", "#27AE60", "#F39C12")

ggplot(race_data_happy3, aes(x = Year, y = People, fill = Race)) +
  geom_line(aes(group = Race, color = Race), size = 1.2) +
  scale_fill_manual(values = race_colors) +
  scale_color_manual(values = race_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Race", title = "Trends in happiness level (not too happy) by race from 1972 to 2021")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-8LessHighSchool
#| fig-cap: "Changes in happiness levels of individuals with less than high school education from 1972 to 2021"

# calcualte the people who have less than high school degree based on different level of happy
degree_data_1 <- degree_data %>% 
  filter(Degree == "Less than high school") %>% 
  group_by(Year, Happy) %>% 
  summarize(People = n())

# generate graph
degree_colors <- c("#E74C3C", "#F1C40F", "#8E44AD")

ggplot(degree_data_1, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith less than high school education from 1972 to 2021", color = "Happy level")

```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-9HighSchool
#| fig-cap: "Changes in happiness levels of individuals with high school education from 1972 to 2021"

# calcualte the people who have high school degree based on different level of happy
degree_data_2 <- degree_data %>% 
  filter(Degree == "High school") %>% 
  group_by(Year, Happy) %>% 
  summarize(People = n())

# generate graph
degree_colors <- c("#E74C3C", "#F1C40F", "#8E44AD")

ggplot(degree_data_2, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith high school education from 1972 to 2021", color = "Happy level")

```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-10AssociateCollege
#| fig-cap: "Changes in happiness levels of individuals with associate/junior college education from 1972 to 2021"

# calcualte the people who have associate/junior college degree based on different level of happy
degree_data_3 <- degree_data %>% 
  filter(Degree == "Associate/junior college") %>% 
  group_by(Year, Happy) %>% 
  summarize(People = n())

# generate graph
degree_colors <- c("#E74C3C", "#F1C40F", "#8E44AD")

ggplot(degree_data_3, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith associate/junior college education from 1972 to 2021", color = "Happy level")
```

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-11Bachelor
#| fig-cap: "Changes in happiness levels of individuals with bachelor's education from 1972 to 2021"

# calcualte the people who have Bachelor's degree based on different level of happy
degree_data_4 <- degree_data %>% 
  filter(Degree == "Bachelor's") %>% 
  group_by(Year, Happy) %>% 
  summarize(People = n())

# generate graph
degree_colors <- c("#E74C3C", "#F1C40F","#8E44AD")

ggplot(degree_data_4, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith bachelor's education from 1972 to 2021", color = "Happy level")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-12Graduate
#| fig-cap: "Changes in happiness levels of individuals with graduate education from 1972 to 2021"

# calcualte the people who have graduate degree based on different level of happy
degree_data_5 <- degree_data %>% 
  filter(Degree == "Graduate") %>% 
  group_by(Year, Happy) %>% 
  summarize(People = n())

# generate graph
degree_colors <- c("#E74C3C", "#F1C40F","#8E44AD")

ggplot(degree_data_5, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = degree_colors) +
  scale_color_manual(values = degree_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Happy level", title = "Changes in happiness levels of individuals \nwith graduate education from 1972 to 2021", color = "Happy level")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-13EmployeeStatusVeryHappy
#| fig-cap: "Trends in happiness level (very happy) by employee status from 1972 to 2021"

# calcualte the number of employee status for very happy
employee_status_data_happy1 <- employee_status_data %>% 
  filter(Happy == "Very happy") %>% 
  group_by(Employee_status, Year, Happy) %>% 
  summarize(People = n())

# generate graph
employee_status_colors <- c("#E74C3C", "#2C3E50")

ggplot(employee_status_data_happy1, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Trends in happiness level (very happy) by employee status from 1972 to 2021", color = "Employee status")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-14EmployeeStatusPrettyHappy
#| fig-cap: "Trends in happiness level (pretty happy) by employee status from 1972 to 2021"

# calcualte the number of employee status for pretty happy
employee_status_data_happy2 <- employee_status_data %>% 
  filter(Happy == "Pretty happy") %>% 
  group_by(Employee_status, Year, Happy) %>% 
  summarize(People = n())

# generate graph
employee_status_colors <- c("#E74C3C", "#2C3E50")

ggplot(employee_status_data_happy2, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Trends in happiness level (pretty happy) by employee status from 1972 to 2021", color = "Employee status")
```

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-15EmployeeStatusNotTooHappy
#| fig-cap: "Trends in happiness level (not too happy) by employee status from 1972 to 2021"

# calcualte the number of employee status for not to happy
employee_status_data_happy3 <- employee_status_data %>% 
  filter(Happy == "Not too happy") %>% 
  group_by(Employee_status, Year, Happy) %>% 
  summarize(People = n())

# generate graph
employee_status_colors <- c("#E74C3C", "#2C3E50")

ggplot(employee_status_data_happy3, aes(x = Year, y = People, fill = Employee_status)) +
  geom_line(aes(group = Employee_status, color = Employee_status), size = 1.2) +
  scale_fill_manual(values = employee_status_colors) +
  scale_color_manual(values = employee_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Employee status", title = "Trends in happiness level (not too happy) by employee status from 1972 to 2021", color = "Employee status")
```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-16MaritalStatusVeryHappy
#| fig-cap: "Trends in Happiness Level (very happy) by Marital Status from 1972 to 2021"

# calcualte the number of marital status for very happy
marital_status_data_happy1 <- marital_status_data %>% 
  filter(Happy == "Very happy") %>% 
  group_by(Marital_status, Year, Happy) %>% 
  summarize(People = n())

# generate graph
marital_status_colors <- c("#E74C3C", "#F1C40F","#2ECC71","#3498DB","#8E44AD")

ggplot(marital_status_data_happy1, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Trends in happiness level (very happy) by marital status from 1972 to 2021", color = "Marital status")
```
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-17MaritalStatusPrettyHappy
#| fig-cap: "Trends in happiness level (pretty happy) by marital status from 1972 to 2021"

# calcualte the number of marital status for pretty happy
marital_status_data_happy2 <- marital_status_data %>% 
  filter(Happy == "Pretty happy") %>% 
  group_by(Marital_status, Year, Happy) %>% 
  summarize(People = n())

# generate graph
marital_status_colors <- c("#E74C3C", "#F1C40F","#2ECC71","#3498DB","#8E44AD")

ggplot(marital_status_data_happy2, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Trends in happiness level (pretty happy) by marital status from 1972 to 2021", color = "Marital status")
```

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-18MaritalStatusNotTooHappy
#| fig-cap: "Trends in happiness level (not too happy) by marital status from 1972 to 2021"

# calcualte the number of marital status for not too happy
marital_status_data_happy3 <- marital_status_data %>% 
  filter(Happy == "Not too happy") %>% 
  group_by(Marital_status, Year, Happy) %>% 
  summarize(People = n())

# generate graph
marital_status_colors <- c("#E74C3C", "#F1C40F","#2ECC71","#3498DB","#8E44AD")

ggplot(marital_status_data_happy3, aes(x = Year, y = People, fill = Marital_status)) +
  geom_line(aes(group = Marital_status, color = Marital_status), size = 1.2) +
  scale_fill_manual(values = marital_status_colors) +
  scale_color_manual(values = marital_status_colors) +
  labs(x = "Year", y = "Number of respondents", fill = "Marital status", title = "Trends in happiness level (not too happy) by marital status from 1972 to 2021", color = "Marital status")
```

>>>>

# loading in relevant libraries
library(cowplot)
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
library(scales)

@@

fig1 <- ggplot(happiness_data, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       color = "Happy level")
fig1 <- fig1  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 12,
             x = 0.5,
             y = 1.05)
fig1
```

```{r, fig.height=6}
#| message: false
#| warning: false
#| echo: false
#| label: fig-2Gender
#| fig-cap: "Trends in happiness levels for different genders from 1972 to 2021"

# Only for female
female_data <- filter(sex_data, Sex == "Female")
gfemale <- ggplot(female_data, 
       aes(y = Year, 
           fill = Happy_level)) + 
  geom_bar(position = "fill") + 
  theme_classic() +
  coord_flip()+
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Female",
       color = "Happy level")

# Only for male
male_data <- filter(sex_data, Sex == "Male")
gmale <- ggplot(male_data, 
       aes(y = Year, 
           fill = Happy_level)) + 
  geom_bar(position = "fill") + 
  theme_classic() +
  coord_flip()+
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       title = "Male",
       color = "Happy level")

# group graphs together
fig2 <- plot_grid(gfemale, gmale, ncol = 1,
          label_size = 12,
          label_x = 0.05,
          label_y = 0.9,
          label_fontface = "bold",
          hjust = 0)

fig2 <- fig2  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig2
```

```{r, fig.height=8}
#| message: false
#| warning: false
#| echo: false
#| label: fig-3Race
#| fig-cap: "Trends in happiness levels for different races from 1972 to 2021"

# Only for white
white_data <- filter(race_data, Race == "White")
gwhite <- ggplot(white_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "White people",
           color = "Happy level")

# Only for black
black_data <- filter(race_data, Race == "Black")
gblack <- ggplot(black_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip()+
      labs(y = "Year", x = "Percentages", fill = "Happy Level", 
           title = "black people",
           color = "Happy level")

# Only for others
others_data <- filter(race_data, Race == "Others")
gothers <- ggplot(others_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "other race",
           color = "Happy level")

# group graphs together
fig3 <- plot_grid(gwhite, gblack, gothers, ncol = 1,
          label_size = 14,
          label_x = 0.05,
          label_y = 0.9,
          label_fontface = "bold",
          hjust = 0)

fig3 <- fig3  +
  draw_label("Trends in happiness levels for different races from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig3

@@

```{r, fig.height=16}
#| message: false
#| warning: false
#| echo: false
#| label: fig-4Degree
#| fig-cap: "Trends in happiness levels for different degrees from 1972 to 2021"

# graph for less than high school
less_high_school_data <- filter(degree_data, Degree == "Less than high school")
glesshighschool <- ggplot(less_high_school_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Less than high school",
           color = "Happy level")

# graph for high school
high_school_data <- filter(degree_data, Degree == "High school")
ghighschool <- ggplot(high_school_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "High school",
           color = "Happy level")

# graph for associate/junior college
junior_data <- filter(degree_data, Degree == "Associate/junior college")
gjunior <- ggplot(junior_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Associate/junior college",
           color = "Happy level")

# graph for bachelor
bachelor_data <- filter(degree_data, Degree == "Bachelor's")
gbachelor <- ggplot(bachelor_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Bachelor",
           color = "Happy level")

# graph for graduate
graduate_data <- filter(degree_data, Degree == "Graduate")
graduate<- ggplot(graduate_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Graduate",
           color = "Happy level")

# group graphs together
fig4 <- plot_grid(glesshighschool, ghighschool, gjunior, gbachelor, graduate, ncol = 1,
          label_size = 14,
          label_x = 0.05,
          label_y = 0.9,
          label_fontface = "bold",
          hjust = 0)

fig4 <- fig4  +
  draw_label("Trends in happiness levels for different degrees from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig4
```

```{r, fig.height=8}
#| message: false
#| warning: false
#| echo: false
#| label: fig-5Employee
#| fig-cap: "Trends in happiness levels for different emoloyee status from 1972 to 2021"

# graph for self-employee
self_data <- filter(employee_status_data, Employee_status == "Self-employed")
gself<- ggplot(self_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Self-employed",
           color = "Happy level")

# graph for someone else
someone_data <- filter(employee_status_data, Employee_status == "Someone else")
gsomeone <- ggplot(someone_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Someone else",
           color = "Happy level")

# group graphs together
fig5 <- plot_grid(gself, gsomeone, ncol = 1,
          label_size = 14,
          label_x = 0.05,
          label_y = 0.9,
          label_fontface = "bold",
          hjust = 0)

fig5 <- fig5  +
  draw_label("Trends in happiness levels for different emoloyee status from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig5
```

```{r, fig.height=16}
#| message: false
#| warning: false
#| echo: false
#| label: fig-6Marital
#| fig-cap: "Trends in happiness levels for different marital status from 1972 to 2021"

# graph for married
married_data <- filter(marital_status_data, Marital_status == "Married")
gmarried_data <- ggplot(married_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Married",
           color = "Happy level")

# graph for widowed
widowed_data <- filter(marital_status_data, Marital_status == "Widowed")
gwidowed_data <- ggplot(widowed_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Widowed",
           color = "Happy level")

# graph for divorced
divorced_data <- filter(marital_status_data, Marital_status == "Divorced")
gdivorced_data <- ggplot(divorced_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Divorced",
           color = "Happy level")

# graph for separated
separated_data <- filter(marital_status_data, Marital_status == "Separated")
gseparated_data <- ggplot(separated_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Separated",
           color = "Happy level")

# graph for never married
never_married_data <- filter(marital_status_data, Marital_status == "Never married")
gnever_married<- ggplot(never_married_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Never married",
           color = "Happy level")

# group graphs together
fig6 <- plot_grid(gmarried_data, gnever_married, gwidowed_data, gdivorced_data, gseparated_data, ncol = 1,
          label_size = 14,
          label_x = 0.05,
          label_y = 0.9,
          label_fontface = "bold",
          hjust = 0)

fig6 <- fig6  +
  draw_label("Trends in happiness levels for different emoloyee status from 1972 to 2021", 
             fontface = "bold", 
             size = 16,
             x = 0.5,
             y = 1.05)
fig6
```
